% Emanuel E. Heitlinger - Curriculum Vitae
%

\documentclass[10pt,a4paper]{article}
\usepackage{hyperref}
\usepackage{geometry}

% Fonts
\usepackage[T1]{fontenc}

%\usepackage[urw-garamond]{mathdesign}
\usepackage{eurosym}


% Set your name here
\def\name{Emanuel Heitlinger}

\geometry{
  body={6.5in, 9.0in},
  left=1.0in,
  top=1.0in
}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {evolution, ecology, host-parasite interactions,
    transcriptomics, genomics},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

% Customize page headers
\pagestyle{myheadings}
\usepackage{sectsty}
\markright{\name}
\pagestyle{empty}

% Custom section fonts
%\sectionfont{\rmfamily\mdseries\Large}
%\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets and compact spacing
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{2.5em}
    \setlength{\itemsep}{0.25em}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0.25em}
  }
}{
  \end{list}
}


% Place name at left
\begin{document}
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\bigskip

\begin{minipage}[t]{0.5\textwidth}
  Geisbergstr. 31 \\
  10777 Berlin \\
  Germany
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
  Phone: (+49) (0)178 2545475 \\
  Email: \href{mailto:emanuelheitlinger@gmail.com}{emanuelheitlinger@gmail.com} \\
  Born September, 12th 1980 in Schw\"abisch Gm\"und, Germany\\
\end{minipage}

\section*{Education}

\begin{itemize}
\item [Jun 2008 - Feb 2012] Doctoral studies, Karlsruhe Institute of Technology.\\
  \textbf{Dissertation:} 
  \href{http://digbib.ubka.uni-karlsruhe.de/volltexte/1000027222}
  {Divergence of an introduced population
    of the swimbladder-nematode \textit{Anguillicola crassus} - a
    transcriptomic perspective.}\\
  \textbf{Supervisors:}
  Prof. Dr. Horst Taraschewski and Prof. Mark Blaxter.
\item [Jun 2007 - Feb 2008] Work on diploma thesis, University of Karlsruhe,
  Zoological Institute, Department for Parasitology and Ecology.\\
  \textbf{Thesis title:} Vergleichende licht- und
  elektronenmikroskopische Untersuchungen am Intestinaltrakt des
  invasiven Schwimmblasennematoden \textit{Anguillicola crassus} aus
  verschiedenen Aalarten.
\item [2001 - 2007] Undergraduate studies in Biology, University of
  Karlsruhe.\\
  \textbf{Main subject:} Zoology\\
  \textbf{Subsidiary subjects:} Genetics, Botany
\item [1991 - 2000] Secondary school, Gymnasium St.Paulusheim
  Bruchsal.
\item [1987 - 1991] Pirmary school, Kraichtal Ober\"owisheim.
\end{itemize}

\section*{Employment}

\begin{itemize}
\item [May 2014 - now] Juniorprofessor, Humboldt University of
  Berlin, Institute for Biology, Department for Molecular
  Parasitology and Leibniz Institute for Zoo and Wildlife research.
\item [March 2012 - May 2014] Postdoctoral researcher, Humboldt University of
  Berlin, Institute for Biology, Department for Molecular
  Parasitology.
\item [Jun 2008- Jul 2011] Research assistant, Karlsruhe Institute of
  Technology, Zoological Institute, Department for Parasitology and
  Ecology.
\end{itemize}


\section*{Fields of Research Interest}
Ecology and evolution of host-parasite interactions, transcriptomics
and genomics

\section*{Research}

\subsection*{Peer Reviewed Publications}

\begin{itemize}


\item \textbf{Emanuel Heitlinger}, Simone Spork, Richard Lucius and Christoph
  Dieterich (2014) The genome of \textit{Eimeria falciformis} -
    reduction and specialization in a single host apicomplexan
    parasite. BMC Genomics, under review.

\item Manuela Schmid, \textbf{Emanuel Heitlinger}, Simone Spork, Hans-Joachim
  Mollenkopf, Richard Lucius, and Nishith Gupta (2013)
  \href{http://www.nature.com/mi/journal/vaop/ncurrent/full/mi2013115a.html}
  {\textit{Eimeria falciformis} infection of the mouse caecum identifies
    opposing roles of IFNγ-regulated host pathways for the parasite
    development.} Mucosal immunology, 25 December.

\item Urszula Weclawski, \textbf{Emanuel Heitlinger}, Tobias Baust,
  Bernhard Klar, Trevor Petney, Yu San Han and Horst Taraschewski
  (2013) 
  \href{http://www.biomedcentral.com/1471-2148/13/78}{
    Evolutionary divergence of the swim bladder nematode
    \textit{Anguillicola crassus} after colonization of a novel host,
    Anguilla anguilla.} BMC Evolutionary Biology,
  13:78.

\item \textbf{Emanuel Heitlinger}, Stephen Bridgett, Anna Montazam,
  Horst Taraschewski and Mark L Blaxter (2013)
  \href{http://www.biomedcentral.com/1471-2164/14/87}{The
    transcriptome of the invasive eel swimbladder nematode parasite
    \textit{Anguillicola crassus}.} BMC Genomics, 
  14:87.

\item Dominik R Laetsch, \textbf{Emanuel Heitlinger}, Horst
  Taraschewski, Steven A Nadler and Mark L Blaxter (2012)
  \href{http://www.biomedcentral.com/1471-2148/12/60} {The
    phylogenetics of Anguillicolidae (Nematoda: Anguillicolidea),
    swimbladder parasites of eels.} BMC Evolutionary Biology,
  12:60.

\item \textbf{Emanuel Heitlinger}, Dominik R Laetsch, Urszula
  Weclawski, Yu-San Han and Horst Taraschewski (2009)
  \href{http://www.parasitesandvectors.com/content/2/1/48}{Massive
    encapsulation of larval \textit{Anguillicoloides crassus} in the
    intestinal wall of Japanese eels}. Parasites \& Vectors,
  2:48.
\end{itemize}

% \subsection*{Scientific Software}
%
% \begin{itemize}
% \item \href{http://foo}{foo},
%   A R package
% \end{itemize}

% \subsection*{Other Publications}
% \begin{itemize}
% \item A book
% \end{itemize}


\subsection*{Conference Presentations}

\begin{itemize}

\item 25th Biannual conference of the German society of parasitology
  (DGP), March 14-17 2012, Heidelberg, Germany. Oral presentation:
  ``Divergence of an introduced population of \textit{Anguillicola
    crassus} a transcriptomic perspective''.

\item 3rd Status Symposium, Volkswagen Foundation Funding Initiative
  Evolutionary Biology, November 7-11 2011, Sylt, Germany. Oral
  presentation: ``Divergence of an intoduced parasite: a
  transcriptomic perspective on \textit{Anguillicola crassus}''.

\item 2nd Status Symposium, Volkswagen Foundation Funding Initiative
  Evolutionary Biology, May 9-12 2010, Frauenchiemsee, Germany. Oral
  presentation: ``The transcriptome of \textit{Anguillicoloides
    crassus} sampled by pyrosequencing''.

\item 24th Biannual conference of the German society of parasitology
  (DGP), March 16-19 2010, M\"unster, Germany. Two oral presentations:
  ``The transcriptome of \textit{Anguillicoloides crassus} sampled by
  pyrosequencing'' and ``Massive encapsulation of larval
  \textit{Anguillicoloides crassus} in the intestinal wall of the
  Japanese eel''.

\item Mind the gap: joining empirical and theoretical population
  genetics, October 2-3 2009, Freiburg, Germany. Oral presentation:
  ``Divergence between European and Asian populations of the
  swimbladder nematode \textit{Anguillicoloides crassus}''.

\item 1st Status Symposium, Volkswagen Foundation Funding Initiative
  Evolutionary Biology, February 25-27 2009, M\"unster,
  Germany. Poster: ``Divergence between East Asian and European
  populations of the swimbladder-nematode \textit{Anguillicola
    crassus}''.

\item Xth European Multicolloquium of Parasitology - EMOP 10, August
  24-28, 2008, Paris, France. Oral Presentation: ``Divergence between
  East Asian and European populations of the swimbladder-nematode
  \textit{Anguillicola crassus}''.

\end{itemize}

% \section*{Professional Activities}
% \begin{itemize}
% \item Reviewer for:\newline
%   \textit{The Journal of Parasitology}\newline
%   \textit{Parasitology research}
%   % Faculty Recruiting Committee (2010-11, 2
%   % G.S. Maddala Prize Committee (2010-11).
%   % \item Member, foo, 2006--Present.
%   % \item Member, foo2, 2010--Present.
%   % \end{itemize}
% \end{itemize}

% \section*{Advising}
% \begin{itemize}
% \item Diploma Students (informal advisor):\newline
%   Dominik Laetsch (2010)\newline
%   Corinna Kieffer (2011)
% \end{itemize}

% \section*{Teaching}
% \begin{itemize}
% \item Support for ZIBI International Summer School on Pathogen-Host
%   Interplay (2012)
% \item Oberseminar Parasitologie (2012 and 2013)
% \end{itemize}

\section*{Honors, Awards, \& Fellowships}

\begin{itemize}
\item [2008] Volkswagen Stiftung PhD Fellowship, Funding Initiative
  Evolutionary Biology, full funding of research position and research
  material (\euro 131k)
\end{itemize}

% \section*{Miscellaneous}

% \begin{itemize}
% \item \textit{Security Clearance:} Special agent.
% \end{itemize}

% Footer
% \begin{center}
%   \begin{small}
%     Last updated: \today
%   \end{small}
% \end{center}

\end{document}
