% Emanuel E. Heitlinger - Curriculum Vitae
%

\documentclass[10pt,a4paper]{article}
\usepackage{hyperref}
\usepackage{geometry}

% Fonts
\usepackage[T1]{fontenc}

\usepackage[urw-garamond]{mathdesign}
\usepackage{eurosym}


% Set your name here
\def\name{Emanuel Heitlinger}

\geometry{
  body={6.5in, 9.0in},
  left=1.0in,
  top=1.0in
}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {evolution, ecology, host-parasite interactions,
    transcriptomics, genomics},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

% Customize page headers
\pagestyle{myheadings}
\usepackage{sectsty}
\markright{\name}
\pagestyle{empty}

% Custom section fonts
%\sectionfont{\rmfamily\mdseries\Large}
%\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets and compact spacing
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{2.5em}
    \setlength{\itemsep}{0.25em}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0.25em}
  }
}{
  \end{list}
}


% Place name at left
\begin{document}
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\bigskip

\begin{minipage}[t]{0.5\textwidth}
  Geisbergstr. 31 \\
  10777 Berlin \\
  Deutschland
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
  Tel.: (+49) (0)178 2545475 \\
  E-Mail: \href{mailto:emanuelheitlinger@gmail.com}{emanuelheitlinger@gmail.com} \\
  geboren am 12.  September 1980 in Schw\"abisch Gm\"und, Deutschland\\
\end{minipage}

\section*{Ausbildung}

\begin{itemize}
\item [Jun 2008 - Feb 2012] Doktorarbeit, Karlsruher Institut f\"ur Technologie.\\
  \textbf{Dissertation:} 
  \href{http://digbib.ubka.uni-karlsruhe.de/volltexte/1000027222}
  {Divergence of an introduced population
    of the swimbladder-nematode \textit{Anguillicola crassus} - a
    transcriptomic perspective.}\\
  \textbf{Betreuer:}
  Prof. Dr. Horst Taraschewski und Prof. Mark Blaxter.
\item [Jun 2007 - Feb 2008] Diplomarbeit, Universit\"at Karlsruhe,
  Zoologisches Institut, Abt. Parasitologie und \"Okologie.\\
  \textbf{Titel der Arbeit:} Vergleichende licht- und
  elektronenmikroskopische Untersuchungen am Intestinaltrakt des
  invasiven Schwimmblasennematoden \textit{Anguillicola crassus} aus
  verschiedenen Aalarten.
\item [2001 - 2007] Studium der Biologie, Universit\"at Karlsruhe.\\
  \textbf{Hauptfach:} Zoologie\\
  \textbf{Nebenf\"acher:} Genetik, Botanik
\item [1991 - 2000] Gymnasium St.Paulusheim, Bruchsal.
\item [1987 - 1991] Grundschule Kraichtal Ober\"owisheim.
\end{itemize}

\section*{Besch\"aftigung}

\begin{itemize}
\item [M\"arz 2012 - now] Post-Doktorand, Humboldt Universit\"at zu
  Berlin, Institut f\"ur Biologie, Lehrstuhl f\"ur Molekulare
  Parasitologie.
\item [Jun 2008- Jul 2011] Doktorand, Karlsruher Institut f\"ur
  Technologie, Zoologisches Institut, Abt. f\"ur Parasitologie und
  \"Okologie.
\item [2000-2001] Zivildienst, Jugendzentrum Bruchsal.
\end{itemize}


\section*{Forschungsinteressen}
\"Okologie und Evolution von Wirt-Parasit Interaktionen, Transkriptomik,
Genomik; genauere Ausf\"uhrungen auf den vorangehenden Seiten.

\section*{Publikationen}

\subsection*{In Zeitschriften mit Begutachtung}

\begin{itemize}

\item Urszula Weclawski, Emanuel Heitlinger, Tobias Baust,
  Bernhard Klar, Trevor Petney, Yu San Han and Horst Taraschewski
  (2013) 
  \href{http://www.biomedcentral.com/1471-2148/13/78}{
    Evolutionary divergence of the swim bladder nematode
    Anguillicola crassus after colonization of a novel host,
    Anguilla anguilla.} BMC Evolutionary Biology,
  13:78.

\item Emanuel Heitlinger, Stephen Bridgett, Anna Montazam,
  Horst Taraschewski and Mark L Blaxter (2013)
  \href{http://www.biomedcentral.com/1471-2164/14/87}{The
    transcriptome of the invasive eel swimbladder nematode parasite
    Anguillicola crassus} BMC Genomics, 
  14:87.

\item Dominik R Laetsch, Emanuel Heitlinger, Horst
  Taraschewski, Steven A Nadler and Mark L Blaxter (2012)
  \href{http://www.biomedcentral.com/1471-2148/12/60} {The
    phylogenetics of Anguillicolidae (Nematoda: Anguillicolidea),
    swimbladder parasites of eels.} BMC Evolutionary Biology,
  12:60.

\item Emanuel G Heitlinger, Dominik R Laetsch, Urszula
  Weclawski, Yu-San Han and Horst Taraschewski (2009)
  \href{http://www.parasitesandvectors.com/content/2/1/48}{Massive
    encapsulation of larval Anguillicoloides crassus in the
    intestinal wall of Japanese eels}. Parasites \& Vectors,
  2:48.
\end{itemize}

% \subsection*{Scientific Software}
%
% \begin{itemize}
% \item \href{http://foo}{foo},
%   A R package
% \end{itemize}

% \subsection*{Other Publications}
% \begin{itemize}
% \item A book
% \end{itemize}


\subsection*{Tagungsbeitr\"age}

\begin{itemize}

\item 25. Tagung der Deutschen Gesellschaft f\"ur
  Parasitologie (DGP), 14-17 M\"arz 2012, Heidelberg. Vortrag:
  ``Divergence of an introduced population of \textit{Anguillicola
    crassus} a transcriptomic perspective''.

\item 3. Status Symposium, Volkswagen F\"orderinitiative
  Evolutionsbiology, 7-11 November 2011, Sylt. Vortrag: ``Divergence
  of an intoduced parasite: a transcriptomic perspective on
  \textit{Anguillicola crassus}''.

\item 2. Status Symposium, Volkswagen F\"orderinitiative
  Evolutionsbiologie, 9-12 Mai 2010, Frauenchiemsee. Vortrag: ``The
  transcriptome of \textit{Anguillicoloides crassus} sampled by
  pyrosequencing''.

\item 24. Tagung der Deutschen Gesellschaft f\"ur Parasitologie (DGP),
  16-19 M\"arz 2010, M\"unster. Zwei Vortr\"age: ``The transcriptome
  of \textit{Anguillicoloides crassus} sampled by pyrosequencing'' und
  ``Massive encapsulation of larval \textit{Anguillicoloides crassus}
  in the intestinal wall of the Japanese eel''.

\item Mind the gap: joining empirical and theoretical population
  genetics, 2-3 October 2009, Freiburg. Vortrag: ``Divergence between
  European and Asian populations of the swimbladder nematode
  \textit{Anguillicoloides crassus}''.

\item 1st Status Symposium, Volkswagen Foundation Funding Initiative
  Evolutionary Biology, February 25-27 2009, M\"unster,
  Germany. Poster: ``Divergence between East Asian and European
  populations of the swimbladder-nematode \textit{Anguillicola
    crassus}''.

\item Xth European Multicolloquium of Parasitology - EMOP 10, August
  24-28, 2008, Paris, France. Vortrag: ``Divergence between
  East Asian and European populations of the swimbladder-nematode
  \textit{Anguillicola crassus}''.

\end{itemize}

\section*{Wissenschaftliche Aktivit\"aten}
\begin{itemize}
\item Reviewer f\"ur:\newline
  \textit{The Journal of Parasitology}\newline
  \textit{Parasitology research}
  % Faculty Recruiting Committee (2010-11, 2
  % G.S. Maddala Prize Committee (2010-11).
  % \item Member, foo, 2006--Present.
  % \item Member, foo2, 2010--Present.
  % \end{itemize}
\end{itemize}

\section*{Betreuung}
\begin{itemize}
\item Diplomanden (informeller Betreuer):\newline
  Dominik Laetsch (2010)\newline
  Corinna Kieffer (2011)
\end{itemize}

\section*{Lehre}
\begin{itemize}
\item Unterst\"utzung der ZIBI International Summer School on Pathogen-Host
  Interplay (2012)
\item Oberseminar Parasitologie (2012 und 2013)
\end{itemize}

\section*{Preise, Auszeichnungen \& F\"ordergelder}

\begin{itemize}
\item [2008] Volkswagen Doktorandenstipendium, F\"orderinitiative
  Evolutionsbiologie, komplette Finanzierung einer \\Mitarbeiterstelle
  und Verbrauchsmaterial (\euro 131K)
\end{itemize}

% \section*{Miscellaneous}

% \begin{itemize}
% \item \textit{Security Clearance:} Special agent.
% \end{itemize}

% Footer
% \begin{center}
%   \begin{small}
%     Last updated: \today
%   \end{small}
% \end{center}

\end{document}
