% Emanuel E. Heitlinger - Curriculum Vitae
%

\documentclass[10pt,a4paper]{article}
\usepackage{hyperref}
\usepackage{geometry}

% Fonts
\usepackage[T1]{fontenc}

% More styles for bullets
\usepackage{pifont}

% \usepackage[urw-garamond]{mathdesign}
\usepackage{eurosym}

% Set your name here
\def\name{Emanuel Heitlinger}

\geometry{
  body={6.5in, 9.0in},
  left=1.0in,
  top=1.0in
}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {evolution, ecology, host-parasite interactions,
    transcriptomics, genomics},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

% Customize page headers
\pagestyle{myheadings}
\usepackage{sectsty}
\markright{\name}
\pagestyle{empty}

% Custom section fonts
%\sectionfont{\rmfamily\mdseries\Large}
%\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets and compact spacing
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{2.5em}
    \setlength{\itemsep}{0.25em}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0.25em}
  }
}{
  \end{list}
}


% Place name at left
\begin{document}
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\bigskip

\begin{minipage}[t]{0.4\textwidth}
  Juniorprofessor
  \begin{itemize}
  \item Humboldt University (HU)
    Department for Molecular Parasitology 
  \item Leibniz Institute for Zoo and
    Wildlife Research (IZW)
    Berlin
  \end{itemize}
\end{minipage}
\hspace{1cm}
\begin{minipage}[t]{0.5\textwidth}
  \bigskip
  \begin{itemize}
%  \item Phone (HU): (+49) (0)30 2093 6450 
%  \item Phone (IZW): (+49) (0)30 5168 253 
  \item Mobile: (+49) (0)178 2545475
  \item Email: \href{mailto:emanuelheitlinger@gmail.com}{emanuelheitlinger@gmail.com}
\end{itemize}
\end{minipage}

\section*{Education}

\begin{itemize}
\item [2008 -- 2012] Doctoral studies, Karlsruhe Institute of Technology.
  \begin{itemize}
  \item[\textbf{Dissertation:}]
    \href{http://digbib.ubka.uni-karlsruhe.de/volltexte/1000027222}
    {Divergence of an introduced population
      of the swimbladder-nematode \textit{Anguillicola crassus} - a
      transcriptomic perspective.}
  \item[\textbf{Supervisors:}]
    Prof. Dr. Horst Taraschewski and Prof. Mark Blaxter.
  \end{itemize}
\item [2001 -- 2008] Undergraduate studies in Biology, University of
  Karlsruhe.
  \begin{itemize}
  \item[\textbf{Main subject:}] Zoology with focus on parasitology
  \item[\textbf{Subsidiary subjects:}] Genetics, Botany
  \end{itemize}
\end{itemize}

\section*{Employment}

\begin{itemize}
\item [2014 -- present] \textbf{Juniorprofessor}, Humboldt
  University of Berlin, Institute for Biology, Department for
  Molecular Parasitology and Leibniz Institute for Zoo and Wildlife
  research.
\item [2012 -- 2014] \textbf{Postdoctoral researcher},
  Humboldt University of Berlin, Institute for Biology, Department for
  Molecular Parasitology.
\item [2008 -- 2011] \textbf{Research assistant}, Karlsruhe
  Institute of Technology, Zoological Institute, Department for
  Parasitology and Ecology.
\end{itemize}


% \section*{Fields of Research Interest}
% Ecology and evolution of host-parasite interactions, transcriptomics
% and genomics, molecular evolution.

\section*{Research}

\subsection*{Selected relevant publications (4 of \~30 total)}

\begin{itemize}

\item  [\ding{54}] Ankur Midha, Víctor Hugo Jarquín-Díaz, Friederike Ebner, Ulrike
  Löber, Rima Hayani, Arkadi Kundik, Alessio Cardilli, \textbf{Emanuel
    Heitlinger*}, Sofia Kirke Forslund*, Susanne Hartmann* (2022)
  \textit{Guts within guts: the microbiome of the intestinal helminth
    parasite Ascaris suum is derived but distinct from its
    host}. Microbiome
  10(1):229. \href{https://doi.org/10.1186/s40168-022-01399-5}{10.1186/s40168-022-01399-5}
  *shared corresponding authors

\item [\ding{51} \ding{164}] Parnika Mukherjee, Gaétan Burgio, \textbf{Emanuel Heitlinger}
  (2021) \textit{Dual RNA Sequencing Meta-analysis in Plasmodium
  Infection Identifies Host-Parasite Interactions}. MSystems
  6,2. \href{https://doi.org/10.1128/msystems.00182}{10.1128/msystems.00182}
  
\item [\ding{164}] Totta Ehret, Simone Spork, Christoph Dieterich, Richard Lucius
  and \textbf{Emanuel Heitlinger} (2017) \textit{Dual RNA-seq Reveals
    No Plastic Transcriptional Response Of The Coccidian Parasite
    Eimeria falciformis To Host Immune Defences}. BMC Genomics 18,
  686. \href{https://doi.org/10.1186/s12864-017-4095-6}{10.1186/s12864-017-4095-6}
  
\item [\ding{51} \ding{71}] \textbf{Emanuel Heitlinger}, Simone Spork, Richard Lucius,
  and Christoph Dieterich. (2014) \textit{The Genome of Eimeria
    falciformis - Reduction and Specialization in a Single Host
    Apicomplexan Parasite}. BMC Genomics
  15,696. \href{https://doi.org/10.1186/1471-2164-15-696}{10.1186/1471-2164-15-696}
  
\end{itemize}
\ding{51} Cross-species orthologs, \ding{71} Genomics, \ding{164} Transciptomics, \ding{54} Metagenomics


\subsection*{More information (click!)}
 \href{https://github.com/derele}{GitHub},
 \href{https://scholar.google.com/citations?hl=en&user=ZgBJ3aAAAAAJ&view_op=list_works&sortby=pubdate}{Google
   Scholar},
 \href{https://www.researchgate.net/profile/Emanuel-Heitlinger}{ResearchGate},
 \href{https://orcid.org/0000-0002-7139-3425}{ORCID}
 \end{itemize}


\end{document}
